---
title: "Assignment 3"
author: "Annika Leiby"
date: "2/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# attach packages

library(tidyverse)
library(dplyr)
```

### While Loop: 

Consider a situation where you want to repeat a function until a condition is met. 

If depth to groundwater in a well increases by 10 meters per year, how many years will it take for the water level in the well to be greater than 80 meters, if the current depth to groundwater is 10 meters?

```{r}

source("while_loop.R")


# What is the depth to groundwater 

depth_groundwater 

# What is the year that depth to groundwater is reached

yr

```

 It will take 23 years for the depth to groundwater to be greater than 80 meters if the depth increases by 10% each year with an inital depth to groundwater of 10 meters. 
 
 
### Case When:

If groundwater (x) is < 40m the groundwater is considered sustainable. If groundwater (x) is == 40m the groundwater is considered overdrafted. If groundwater (x) is > 40m, the groundwater is considered critically overdrafted.

You have four wells with  different depths to groundwater. Well one has a depth to groundwater of 35m, well two has a depth to groundwater of 40m, well three has a depth to groundwater of 26m, and well four has a depth to groundwater of 79m. What is the groundwater classification of each well?

```{r}

# Set up the well depth inputs
x =c(35,40,26,79)


# Set up the case when function with the groundwater category that is returned based on a given well depth input

case_when(x < 40 ~ "sustainable", x == 40 ~ "overdrafted", x > 40 ~ "critically overdrafted")

# Run to get groundwater categories for the four wells 

```

Well one is classified as having sustainable groundwater levels. Well two is classified as having overdrafted groundwater levels. Well three is classified as having sustainable groundwater levels and well four is classified as having critically overdrafted groundwater levels. 